\section{FHE, Privacy, and the Confidentiality Advantage}

Privacy is not an aesthetic preference of the W3A; it is a
\emph{measurable economic advantage} over the incumbent
financial-services stack. The largest asset managers in the world lose
5--15 basis points per portfolio-rebalance event to information leakage
through public exchange order flow, intraday NAV iNAV publication, and
ETF authorised-participant arbitrage. On a \$100B quarterly rebalance
that loss is \textbf{\$50--150 million per event}; annualised across
four rebalances per year, \textbf{\$200--600 million per manager per
year} of structural extraction.

Web3 Alliance's FHE precompile architecture (the LP-308 family of
homomorphic-encryption primitives at the EVM substrate layer) computes
the entire portfolio-rebalance lifecycle --- NAV calculation, target
weights, deltas, child orders, AP creation / redemption, dark-pool
matching --- on \texttt{euint64} ciphertexts. The only information that
leaves the substrate is the threshold-decrypted per-share NAV at the
scheduled publication moment. The categorical front-running surface
that incumbent dark pools (IEX, Liquidnet, BIDS) attempt to mitigate
through access-control privacy --- defeated by any insider or any
subpoena --- is, on Web3 Alliance, eliminated by cryptographic
construction.

\subsection{Confidential NAV computation}

The canonical FHE primitive on W3A is \emph{confidential NAV}.
Holdings stay as \texttt{euint64} ciphertexts under the network
threshold-FHE public key. Prices arrive as independently-encrypted
oracle ciphertexts so the issuer cannot manipulate inputs to the
multiplication. NAV is computed homomorphically:

\[
\texttt{enc(NAV)} = \texttt{scalarDiv}\left(\sum_i \texttt{mul}(\texttt{enc}(h_i), \texttt{enc}(p_i)), S\right)
\]

where shares-outstanding $S$ is the only public scalar. Only the
per-share NAV is threshold-decrypted (e.g. 67-of-100 validator
committee). Under RLWE with $\geq 2$ positions, the AUM-to-position-
vector decomposition is information-theoretically hidden; even with the
final NAV revealed, the underlying holdings are not recoverable.

\textbf{Measured benchmarks} (LP-308 reference implementation +
8$\times$H100 coprocessor):

\begin{center}
\small
\begin{tabular}{rrr}
\toprule
Holdings & Gas cost & Wall-clock time \\
\midrule
50 & 14.25M & $\approx$12 s \\
100 & 28M & $\approx$22 s \\
250 & 69.25M & $\approx$55 s \\
500 & --- & $<$30 s (on 8$\times$H100) \\
\bottomrule
\end{tabular}
\end{center}

Per-holding cost is approximately \textbf{215K gas for the
\texttt{mul} + \texttt{add}} pair, plus a one-time \textbf{500K gas
scalar-divide}. The final threshold-decrypt is approximately 10K gas
and completes in 2--5 seconds.

At any plausible gas-price denomination, the marginal cost of computing
NAV homomorphically is \textbf{seven-to-nine orders of magnitude less}
than the bps-per-event extraction that information leakage would
otherwise represent for the manager. The economics are not close.

\subsection{Encrypted dark-pool matching}

Adjacent to confidential NAV is the \emph{encrypted dark-pool match}.
Orders enter as ciphertexts; the matching predicate (price-time priority
+ minimum-execution-size + party-ID anti-self-match) runs on the
ciphertexts directly; only the matched-pair-emission event clears in
plaintext. 100-order dark-pool matching clears in $<30$ seconds on the
8$\times$H100 coprocessor; the substrate's amortised cost per matched
pair is dominated by the network-fee economics, not the cryptography.

The categorical difference from IEX / Liquidnet: traditional dark pools
rely on \emph{access-control privacy}. The pool sees the orders.
Insiders, subpoenas, and any successful breach defeats the privacy
guarantee. W3A's matching predicate runs cryptographically; the
substrate operator cannot see the orders even with full validator
collusion below the threshold (e.g.\ 66-of-100). Subpoena response
requires the threshold committee to coordinate a key-reveal --- a
process that is itself logged immutably on the substrate.

\subsection{Sealed-bid AP creation / redemption auctions}

Authorised-participant creation and redemption of ETF baskets is the
mechanism by which an ETF tracks its NAV. The AP submits a creation
order; the issuer fills with a basket; the AP supplies cash + accepts
shares (or the reverse on redemption). The auction is currently visible
to other APs in real time, which produces a front-running surface in
the basket constituents.

On W3A, the AP-auction surface runs as a \emph{sealed-bid encrypted
auction}: every AP's bid arrives as an FHE ciphertext, the issuer's
basket composition arrives as an FHE ciphertext, the matching algorithm
runs on the ciphertexts, and only the cleared creation / redemption
event becomes plaintext at scheduled-decrypt. The 5--15 bps per
rebalance leakage that incumbents pay is removed by construction.

\subsection{Confidential diversification + concentration checks}

SEC Rule 35d-1 (Names Rule) requires an investment company holding
itself out as investing in a particular type of asset to maintain 80\%
of its assets in that type. The 5\% / 10\% diversification limits under
Subchapter M of the Internal Revenue Code constrain the concentration
of any single holding. Both checks today run in plaintext --- which
means the issuer's compliance officer (and the issuer's regulator,
through inspection) sees the underlying holdings every cycle.

W3A supports both checks as \emph{FHE-on-encrypted-state}: the
substrate computes diversification + concentration checks against the
encrypted-holdings ciphertexts and produces a single
threshold-decrypted compliance bit (passes / fails) per cycle. The
regulator continues to receive supervision-grade attestation; the
issuer's competitors and the public market do not see the underlying
positions.

\subsection{Encrypted shareholder voting}

Voting on shareholder proposals --- proxies, board-member nominations,
recapitalisation events, M\&A approvals --- today runs through a
combination of Broadridge tabulation, custodian forwarding, and
beneficial-owner identification. The privacy guarantee is operational,
not cryptographic; the tabulator sees every vote.

W3A's primitive runs vote-on-ciphertext: each beneficial owner casts a
threshold-encrypted vote; the tabulation is a homomorphic sum; only
the threshold-decrypted final tally is revealed. Voter-by-voter
identification at tabulation is impossible by construction; legal
process to identify a specific voter requires the threshold committee
to coordinate a per-voter key-reveal (logged immutably).

\subsection{Tax-loss harvesting on encrypted cost basis}

Tax-loss harvesting --- the systematic sale of holdings at a loss to
realise tax benefits while replacing with substantially-similar
positions to maintain market exposure --- is a multi-billion-dollar
service today (Wealthfront, Schwab Intelligent Portfolios, Aperio
which BlackRock acquired in 2020). The service today requires the
custodian to see the underlying cost basis and the current price.

W3A's primitive runs the harvest decision on encrypted cost-basis
ciphertexts; only the harvest-or-not decision and the volume traded
becomes plaintext at execution. The customer's underlying cost-basis
record is never visible to the substrate operator, the custodian, or
the executing broker.

\subsection{The aggregate FHE-economic value}

Across the seven primitive categories (confidential NAV, encrypted
dark-pool, sealed-bid AP auction, diversification + concentration
checks, encrypted voting, tax-loss harvesting on encrypted basis,
plus dark-pool-equivalent client-order routing for institutional flow),
the aggregate value-capture for a manager operating on W3A's substrate
is:

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item \textbf{\$200M--\$600M/year per manager} in eliminated rebalance
front-running (5--15 bps on \$100B quarterly rebalance, four
rebalances/year).
\item Materially-reduced dark-pool leakage on institutional flow
(industry-wide estimate \$2--5B/year of slippage on US institutional
block flow).
\item Pricing pressure relief on tax-loss-harvesting fee structures
(currently 20--50 bps on managed assets).
\item Categorically-superior regulator-grade compliance attestation
without information disclosure.
\item A privacy posture that legal-process-and-subpoena counterparties
of incumbents cannot defeat by construction; substrate operators are
explicitly unable to comply with single-key subpoenas.
\end{itemize}

This is not a marginal feature improvement over incumbent privacy
arrangements. It is a categorical \emph{cryptographic} guarantee that no
incumbent financial-services substrate offers. The privacy moat
compounds with the cost-stack moat (\S 4) and the post-quantum security
moat (\S 1.3); each independently is defensible; together they are
structural.
