\section{The Great Crossover --- Market Sizing and Liquidity Migration}

The economic case for the Alliance presumes that a meaningful fraction
of the world's financial assets, payment flows, and trading volume
migrates onto decentralized rails over the next 5--15 years. This
section quantifies the addressable market and the rate of capital
migration that the Alliance is positioned to capture.

\subsection{Global financial asset base --- the denominator}

The addressable market is not measured in billions. It is measured in
hundreds of trillions of dollars of financial assets globally:

\begin{table}[H]
\centering
\small
\begin{tabularx}{\textwidth}{X r r}
\toprule
\textbf{Asset category} & \textbf{Global AUM} & \textbf{2025 baseline}\\
\midrule
Total global financial assets & \$486T & BIS / FSB / Allianz aggregate\\
Listed equity (all major markets) & \$115T & WFE \\
Fixed income (sovereign + corporate + securitized) & \$130T & ICMA / SIFMA \\
Bank deposits (global, all currencies) & \$95T & BIS \\
Real estate (residential + commercial) & \$326T & Savills \\
Commodities (oil + gas + metals + softs) & \$5--8T & WGC + LBMA + LME \\
Insurance + pensions AUM & \$80T & OECD pension stats \\
\midrule
Total payment flow (annual, global) & \$2,000T+ & SWIFT + ACH + RTGS \\
Cross-border payments (annual) & \$190T & McKinsey + BIS CPMI \\
Foreign exchange (BIS triennial, daily turnover) & \$7.5T/day & BIS \\
\midrule
Crypto market cap (2026 baseline) & \$2--3T & CMC \\
Stablecoin float (2026 baseline) & \$250B & DefiLlama \\
Tokenized RWA float (2026 baseline) & \$15B & rwa.xyz / Galaxy \\
\bottomrule
\end{tabularx}
\caption{Global financial-asset and payment-flow denominators. The
crypto + tokenized-RWA base is roughly 0.5--0.6\% of the total
financial-asset base today; the migration trajectory below estimates the
addressable size in the 5--15-year horizon.}
\end{table}

The number to internalise is not the crypto float; it is the gap
between the crypto float and the global denominator. A 1\% migration of
the global financial-asset base onto decentralized rails is \$4--5T of
new on-chain TVL. A 10\% migration is \$40--50T --- larger than the
combined balance sheets of the four largest US banks. A 25\% migration
is \$100T+ and is structurally comparable to the position-shift caused
by the introduction of the index-fund and the ETF over the prior 40
years.

\subsection{The migration vectors --- where the flow comes from}

Capital does not migrate all at once or uniformly. It migrates through
specific vectors with specific catalysts. The Alliance is positioned to
capture flow through each:

\textbf{(1) Tokenized Treasuries / money-market funds.} The fastest-
moving vector today. Tokenized US Treasury exposure (BUIDL, USDY,
similar) grew from sub-\$1B in early 2024 to \$10B+ by mid-2025 and
on a trajectory to \$50--100B+ by 2027. The Alliance captures this
flow through (a) the Creatrust / Luxembourg tokenization rail for
non-US-resident demand, (b) NCPS-backed US-eligible tokenized
Treasury issuance, (c) the FHE-confidential primitives for
institutional allocators who require NAV privacy.

\textbf{(2) Stablecoin replacement of correspondent banking.}
Stablecoin float grew from \$3B in 2020 to \$250B+ in 2026. The next
inflection is the migration of cross-border B2B payment flow from
SWIFT correspondent banking (\$190T/yr in cross-border flow, of which
SWIFT carries the bulk) to stablecoin rails. Even a 1\% migration is
\$1.9T/yr of incremental stablecoin transaction volume; the
Alliance's member SSB diaspora-corridor and AvaTrade FX-routing
posture is positioned to capture the diaspora and FX-arbitrage
slices.

\textbf{(3) Tokenized real estate + commodities + private equity.}
The \$326T global real-estate base is the largest single asset class
in dollar terms; its on-chain tokenization rate today is sub-0.01\%.
The structural barriers (legal-title perfection, fractional ownership
mechanics, secondary-market liquidity) are exactly the categories the
Alliance's substrate addresses through ERC-3643 / T-REX + W3A's
captable + transfer-agent stack.

\textbf{(4) Retail brokerage migration.} Equity-trading volume on
retail-facing brokerage platforms (Robinhood, eToro, Webull, Public,
similar) is approaching parity with the institutional flow in some
geographies. The Alliance's GameFi-converted Phase-Two super-app
(\S 8) captures this slice through the same Alliance-member NCPS BD
+ TA + ATS posture used for the institutional flow, with the same
fee economics and the same FHE-privacy guarantees.

\textbf{(5) Asset-management substrate migration.} The Aladdin
incumbent powers a substantial fraction of global asset-management
analytics. As FHE-coprocessor cost falls (the 8$\times$H100 NAV
benchmarks of \S 5 are a 2026 baseline; the cost trajectory is
quasi-linear with GPU-capability improvements), the structural
advantage of FHE-grade analytics over access-control privacy becomes
overwhelming. The Alliance's \texttt{aivm} A-Chain attestation
surface and FHE precompile family is positioned to displace
incumbent-analytics-substrate cost-of-capital line items at the
margin first, then categorically.

\textbf{(6) Sovereign + CBDC interoperability.} Multiple jurisdictions
are pursuing central-bank digital currency programmes (mBridge, the
ECB Digital Euro, the BoE Digital Pound, the SARB Project Khokha).
Each requires interoperability with regulated DeFi counterparties for
the wholesale and cross-border CBDC lanes. The Alliance's posture
across IOM, Luxembourg, Singapore, UAE, and Horn-of-Africa gives it a
defensible position as an early integration counterparty for whichever
of these programmes moves first.

\subsection{The 5-year trajectory --- what we think happens}

We do not predict an exact migration pace; we observe that the
trajectory is steepening. The base case for 2030:

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item Stablecoin float reaches \$2--3T (8--12$\times$ today).
\item Tokenized-RWA float reaches \$1--3T (60--200$\times$ today).
\item On-chain settlement of cross-border payments captures 5--15\% of
the \$190T/yr flow ($\$10$--$\$30T/yr$ of incremental on-chain
settlement volume).
\item DeFi TVL reaches \$300--600B (3--6$\times$ today; constrained by
the on-chain TVL ceiling rather than by capability).
\item Crypto + tokenized assets as fraction of global financial assets
moves from $\sim$0.6\% today to 2--5\%, depending on the rate of
tokenized-RWA expansion (\$10--25T of crypto-and-tokenized AUM).
\end{itemize}

\textbf{The Great Crossover thesis is that the migration is monotone
and accelerating, not cyclical}. The migration accelerates when (a) the
regulatory baseline clarifies further (MiCA already live, SEC ETF /
custody rule trajectory, UK FCA roadmap, MAS / VARA crypto-asset
service-provider regime), (b) tokenized-RWA legal frameworks pass
specific perfection-of-title and on-chain-transferability tests in
US, UK, EU, and Asia courts (in process today), and (c) on-chain
infrastructure matures to the throughput, latency, and FHE-privacy
posture the Alliance's substrate already delivers.

\subsection{What the Alliance captures}

The Alliance does not need to capture 100\% of any of these vectors to
clear the \$100B--\$1T-class enterprise-value target of \S 1.3. The
arithmetic of capture:

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item \textbf{1\% of the 2030 stablecoin float} ($\$2$--$\$3T$
$\rightarrow$ \$20--30B of float on the Alliance substrate at any one
time, with a multiple of that in annual flow).
\item \textbf{1\% of tokenized-RWA float} (\$10--30B AUM on the
Alliance substrate).
\item \textbf{0.5\% of on-chain cross-border settlement} (\$50--150B
annual flow through Alliance-routed corridors).
\item \textbf{2\% of DeFi TVL} (\$6--\$12B in Alliance-LP-
substrate-protected pools).
\item \textbf{0.1\% of the global asset-management substrate}
($\sim$\$0.5T of AUM on the FHE-confidential analytics surface).
\end{itemize}

At Alliance-blended fee economics (low single-digit bps on float-and-
flow, mid-double-digit bps on FHE-confidential analytics-as-a-service,
LP-and-validator fee economics structured per the substrate's reward
formula), \textbf{the aggregate fee revenue at this share is on the
order of \$3--8 billion/year}, before any contribution from the
\$141B/yr-incumbent-cost-extraction story of \S 4. Even at fractional
capture rates, the Alliance is positioned for the enterprise-value
target. Higher capture rates compound proportionally.
