\section{Phase Two --- Conversion to Web3 Financial Super-App}

Phase Two converts the Phase-One consumer user base into customers of a
broader \textbf{web3 financial super-app} spanning payments, custody,
trading, lending, and real-world-asset access. The conversion is the
critical compounding step: without it, the Alliance is a games company
with a chain. With it, the Alliance is a financial-services franchise
with a built-in distribution moat and a fully-validated substrate.

\subsection{Why conversion works}

Three properties of the Phase-One user base make the Phase-Two
conversion structurally favourable.

\textbf{Existing custodial wallet.} Every Phase-One player already holds
an in-platform wallet. Converting that wallet to receive non-game tokens,
hold stablecoins, fund a trading position, or borrow against a holding
requires no new account opening. The friction that defeats most fintech
acquisition campaigns is eliminated.

\textbf{KYC already in place.} The 200,000 KYC-eligible Phase-One wallets
(\S 3.3) have completed identity verification at a level sufficient to
graduate directly into financial products without re-onboarding. The
Alliance pays the KYC cost once and uses it across Phase One and Phase
Two.

\textbf{Behavioural data and trust.} Phase-One users have been making
on-chain transactions inside the Alliance's surface for months. The
Alliance has earned the trust required to broaden into financial products
in a way that a cold-start fintech cannot.

\subsection{The super-app surface}

The Phase-Two super-app is a single mobile and web app that wraps the
Alliance's financial back-end into a unified user experience. The
back-end is the Web3 Alliance stack documented at \texttt{docs.lux.financial}
in production today; the front-end is a thin, brand-themed surface per
member venue. Each capability is exposed as a panel inside the super-app:

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item \textbf{Payments} (cards, ACH, wire, FedNow, SEPA, faster
payments, RTP, stablecoin on/off-ramp, remittance corridors)
--- backed by SF Private Pay, Atmen, the broker stack, M-Pesa, SSB, and
the partner ecosystem.
\item \textbf{Custody} (custodial via W3A MPC + KMS for retail; optional
self-custody for sovereignty-minded users; institutional via the
regulated TA + custody surface).
\item \textbf{Trading} (spot crypto, securities through the regulated US
back-end, FX through the cross-rail forex engine, perpetuals on the W3A
DEX, GPU-accelerated matching for institutional flow).
\item \textbf{Lending} (collateralised against on-chain holdings; rate
discovery on the W3A DEX; settlement on-chain with off-chain enforcement
through the regulated TA layer).
\item \textbf{Real-world assets} (tokenized securities issued through the
regulated US back-end and the Luxembourg / Creatrust platform; commodities;
real estate; fund LP interests; the multi-billion-dollar RWA pipeline
that has been in production on the Luxembourg footprint).
\end{itemize}

Each panel is independently optional per jurisdiction; a customer in
Somalia is offered a different panel mix than a customer in Singapore.
The customer never sees the back-end complexity; the regulatory routing
happens at the Alliance's smart-order router, not at the customer's
choice.

\subsection{Cross-member economics}

The super-app captures fees at every panel. Fee share among the
participating Alliance members is governed by the standard
50/50-above-documented-costs partnership template (\S 7.3 and the
\texttt{partnerships/} record in the Alliance legal estate). Each
member is incentivised to contribute distribution and capability into
the super-app because every member shares in the resulting revenue ---
the network effect is in the cap table, not just in the marketing copy.

\subsection{What success looks like at end of Phase Two}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item \textbf{One million active super-app users} within twenty-four
months of conversion launch.
\item \textbf{\$1 billion assets under custody} across crypto +
securities + RWA by end of month twenty-four.
\item \textbf{\$100 million annualised platform revenue} by end of
month twenty-four.
\item \textbf{Five thousand institutional accounts} (RIAs, family
offices, fund administrators, corporate treasury) onboarded by end of
month twenty-four.
\end{itemize}

These targets are calibrated against the comparable industry trajectory
of analogous super-apps (Revolut, Cash App, Robinhood) but with the
materially favourable starting condition of an existing 500K-active-wallet
base from Phase One and a multi-jurisdiction regulated partner stack
already in place.

\subsection{The capital-position outcome of Phase Two}

A successful Phase Two delivers two compounding assets to Phase Three.
The first is \emph{operating cash flow}: a financial super-app at one
million active users and \$100M annualised revenue throws off material
free cash flow, which feeds Phase-Three acquisitions. The second is
\emph{distribution leverage}: a million-user, multi-jurisdiction,
multi-product surface is the most valuable currency the Alliance can
offer a Phase-Three acquisition target. Members of the network buy
into the Alliance not for the cash check, but for the access to that
distribution.
