\section{Milestones}

The Alliance's progress is measured against the following explicit
milestones. Each milestone is calibrated against the conditions at which
it can credibly be claimed and the asset or metric that demonstrates it.

\subsection{Year 0 (operative now)}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item Substrate production-ready across the Tier-1 / Tier-2 / Tier-3
licensing stack. \textbf{[done]}
\item Patent portfolio catalogued: 87 inventions; 11 filed; 51 filable.
\textbf{[done]}
\item Partner ecosystem documented: SF Private Bank, North Capital,
AvaTrade, Atmen, Salaam Somali Bank, Creatrust, CDAX (IOM).
\textbf{[done]}
\item Clean-room engineering protocol live; provenance trailers
enforced on substrate commits. \textbf{[done]}
\item GameFi platform near-market: fifteen titles instrumented;
experienced team in place.
\item Capital architecture committed: Layer-1 substrate capital
secured; Layer-2 round structures defined.
\item SOC 2 engagement clock started (Type I observation point
projected; Type II report projected on the standard 18-month cadence).
\textbf{[done]}
\end{itemize}

\subsection{Year 1}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item GameFi platform live across mobile / web / desktop.
\item 500,000 monthly active wallets across the slate (Phase-One
metric, \S 3.3).
\item 1M on-chain transactions per day sustained (Phase-One metric).
\item \$25M annualised gross revenue from in-game economies (Phase-One
metric).
\item 200,000 KYC-eligible wallets graduating to Phase-Two eligibility.
\item Super-app architecture and beta cohort defined.
\item Substrate validated at production scale; substrate-validation
record published.
\item SOC 2 Type I report issued.
\item First Phase-Three acquisition diligenced (target close: Year 2 Q1).
\end{itemize}

\subsection{Year 2}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item Super-app launched (general availability across initial
jurisdictions).
\item 1M active super-app users (Phase-Two metric, \S 4.4).
\item \$1B assets under custody across crypto + securities + RWA.
\item \$100M annualised platform revenue.
\item 5,000 institutional accounts onboarded.
\item SOC 2 Type II report issued.
\item One Phase-Three transaction per quarter (target: 4 transactions
across fintech / gaming / RWA / infrastructure).
\end{itemize}

\subsection{Years 3--4}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item Phase-Three cadence ramps to one transaction per month.
\item Cumulative 12--18 Alliance members operating under shared
substrate / IP / distribution.
\item First member-level liquidity event (strategic sale or sub-IPO).
\item Alliance-aggregate revenue \$1B+ run rate.
\item Cross-jurisdiction expansion to all 8+ documented regions
operating at scale.
\end{itemize}

\subsection{Year 5}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item 20 Alliance members.
\item \$10B+ aggregate Alliance revenue.
\item \$100B+ aggregate Alliance enterprise value (low end of
\$100B--\$1T target).
\item 5 member-level public-market liquidity events.
\item Coordination-layer public listing (parent holding) under
review.
\end{itemize}

\subsection{Years 6--7}

\begin{itemize}[leftmargin=2em,itemsep=0.1em]
\item Aggregate enterprise value approaching \$1T (upper bound of
target).
\item Coordination-layer public listing executed (if Year 5 review
supported it).
\item Substrate established as recognised category leader in
post-quantum web3 infrastructure; institutional and sovereign demand
for the substrate exceeds Alliance-internal capacity.
\item Alliance is operating in steady-state compounding: each new
member raises every prior member's enterprise value through documented
network effects; every Phase-Three transaction is priced at the
member-network's marginal addition rather than against external comps.
\end{itemize}

\subsection{Discipline notes on the milestones}

\textbf{Phases gate phases.} Phase Two does not launch until Phase One
clears its metrics. Phase Three does not accelerate until Phase Two
clears its metrics. Skipping the gate in pursuit of headline metrics is
the single most common mode of failure for analogous alliances; the
discipline is to enforce the gate even when external pressure tempts
acceleration.

\textbf{Milestones are floor, not ceiling.} The targets above are the
minimum that justifies the next phase. Exceeding them is encouraged but
does not unlock the next phase early; the gating logic is met-condition,
not best-of-window.

\textbf{Slippage is acknowledged, not hidden.} Any milestone missed by
more than 90 days triggers a coordination-layer review and a written
explanation circulated to members. The discipline is to surface
slippage early, not to backfill metrics or stretch definitions.
